---
title: "Manuscript Outline"
author: "Leigha Aitken"
date: "2025-07-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Embed an R code chunk:

```{r cars} summary(cars)}
```

Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE} plot(pressure)}
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## ABSTRACT

-   250 words

-   6 keywords - alphabetical order

Fisheries modelling can take years of specialist training to learn. Agentic AI systems automate complex computing programming workflows and could lower the technical barrier for fisheries modelling. However, questions remain about the quality of AI derived models. Here we test whether agentic AI can write computer code to complete three common types of fisheries models. We test an agentic AI system (Roo Code) on its ability to complete three fisheries modelling workflows, from data analysis to report write-up: (1) mortality rate estimation, (2) generalized linear modelling of fish-habitat relationships, (3) spawner per recruit analysis. We use replicate prompts and a rubric to evaluate the AI generated reports. We find that... We show how careful prompting of the AI system can deliver high quality reports for fisheries modelling problems. Our results show that agentic AI systems can already complete complex fisheries workflows, particularly if users provide context-rich prompts. We discuss implications for fisheries science including equity of access to technical expertise and the immediate priority of increasing transparency of AI use in fisheries science, potential pitfalls, and the need for a community of practice around prompting.

## Table of contents

## Introduction - NO WORD LIMIT! include line numbers!

-   Include line numbers in main text
-   Species Names: First use - common (genus, species, and famiy name) - eg.Atlantic cod (*Gadus morhua*, Gadidae)

## 1 Methods

### 1.1 Subheadings [not]{.underline} bold

#### 1.1.1 sub-sub headings bold

## 2 Results

-   Tables and figures included at end not in this section

## 3 Discussion

## 4 Conclusion

## Acknowledgements

## Data availability

-   plus link to repository

## Conflict of Interest

## References

## Tables

-   All abbreviations must be defined in footnotes. Footnote symbols: †, ‡, §, ¶, should be used (in that order) and \*, \*\*,\*\*\* should be reserved for P-values
-   **TABLE 1.** xxx

## Figure Legends

-   Figures and supporting info should be supplied as separate files
    -   [electronic_artwork_guidelines.pdf](https://media.wiley.com/assets/7323/92/electronic_artwork_guidelines.pdf)
    -   In-text Figures: **CAPTION 1 (A)** xxx
    -   Supporting information Figures: **Table S1** xxx; **Appendix S1**
-   Include definitions of any symbols used and define/explain all abbreviations and units of measurement
